Transformer based Reading Comprehension model for China Court Cases

### 2021-01-25 A-BasicCommom/ACL2021/acl_comprehension.tex
1.完成阅读理解ACL2021文章

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{509} %  Enter the acl Paper ID here

@@

\begin{document}
\maketitle
\begin{abstract}
 Teaching machines to read court cases remains an elusive challenge.
 In this paper, I proposed a Transformer based model that learn to read real documents and answer complex questions.
 Test on the CJRC2019 dataset, proposed model achieved 2\% improvement on the macro-F1 score compared to the BERT model.

@@

  Progress on the machines reading and understanding documents has been made recently.
  Supervised natural language reading comprehension datasets have been brought recently, \eg \citet{duan2019cjrc}, \citet{cui2019span}.
  \citet{Hermann2015Teaching} observed that summary and paraphrase sentences from the documents can be converted to the context-query-answer pattern.
  In this paper, I emphasize solving the problem that given a context, and a corresponding question, the answer can be generated by the entity detection out of the context,
  or answering the question by affirmative, disagreement, and not-responding.

@@

@@

    There are 39333 training records, 6000 development records, and 6000 test records in the CJRC2019 dataset,
and there are 5053 training records and 1565 test records in the CJRC2020 dataset.

@@

Then from the output of the start and the end position tensors, the maximum possible start and end position were calculated
using the positional probability addition of the all possible start-end pairs.

@@

After the encoding layers, the hidden layers of the BERT layers are kept, and the last two layers are concatenated and connected
two Fully Connected layers for the starting index and the ending index for the answer span indices in the context.

@@

Three losses were added with weighted and then use the stochastic gradient descent to train the network parameters.
The start position loss, the end position loss, the type loss, and the supporting sentence loss were added with weighted.
The start and end loss use the Cross Entropy Loss function, the type uses binary cross entropy with logits,
and the support loss used the binary cross entropy with logits between the output and the gold value, then get the mean of each record.
The support loss has a weight of 5 for its importance in finding the destination answer span, and all other loss has the weight of 1.
And the threshold for the supporting sentence is 0.5.
The learning rate is $5e{-4]}$, the dropout rate is 5\%, the document max sequence length for the document(the question and the context) is 512, and the max sequence length for the question is 45, the epoch size is 10.
The batch size is 16,8, or 4 for the RBT3, RoBERTa-wwm-ext, and RoBERTa-Large model, for the GPU memory limit.

@@

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{cws-architecture.pdf}}
\end{center}
   \caption{The Network Architecture for the Chinese word segment task.}
\label{fig:short}
\end{figure*}

@@

 The MSR Chinese word dataset has 2.37 million words in the training set with 88 thousand vocabulary size,
 and has 107 thousand words in the test set with 13 thousand vocabulary size.
 As \citet{emerson2005second} reported that, during the second international Chinese word segment competition,
the best F1-score achieved was 97.2\% with permission of using the additional corpus on the MSR test dataset.

\subsection{Common Setups}

\begin{table}
\centering
\begin{tabular}{cccc}
\hline
\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{F1} \\
\hline
RBT3 & 768 & 3 & 92.62\% \\
RoBERTa & 768 & 12 & 94.65\% \\
RoBERTa-Large & 1024 & 24 & 97.88\% \\
\hline
\end{tabular}
\caption{Comparison of the pre-trained language models on the MSR2005 Chinese word segement task.}
\end{table}

All the Table (1) models share almost the same network architecture except for the embedding of the tokens.

@@

In this paper, I introduced a novel Chinese word segment architecture, which leveraging hierarchical layers of the document encoding layers.
By keeping the Conditional Random Field layer, I proposed a novel sequence hidden representation of the document sequence, which achieved 3.23\% performance gain in macro F1-score than
the BERT and CRF architecture on the MSR2005 Chinese word segment test dataset.
Not surprisingly, the performance of the proposed XLNet-CRF model also exceed the best result of the Second International Chinese Word Segmentation Competition.

\bibliographystyle{acl_natbib}
\bibliography{anthology,acl2021,acl_word}

>>>>

%\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{1367} %  Enter the acl Paper ID here

@@

\begin{document}
\maketitle
\begin{abstract}
 Teaching machines to read court cases remains an elusive challenge.
 In this paper, I proposed an XLNet based model, and use the Capsule Net as hidden representation layers,
 and use multi-task learning for the question type, start-end indices, and supporting sentence indices,
 thanks to the deep neural architecture, the proposed model learns to read real documents and answer complex questions.
 Test on the CJRC2019 validation dataset, proposed model achieved 1.57\% improvement on the span F1-score and 1.35\% on the supporting sentence F1-score comparing to the BERT model.

@@

  Progress on the machines reading and understanding documents has been made recently.
  Supervised natural language reading comprehension datasets have been brought recently, e.g. CJRC2019 by \citet{duan2019cjrc}, and CMRC2018 by \citet{cui2019span}.
  \citet{Hermann2015Teaching} observed that summary and paraphrase sentences from the documents can be converted to the context-query-answer pattern.
  In this paper, I emphasize solving the problem that given a context, and a corresponding question, the answer can be generated by the entity detection out of the context,
  or answering the question by affirmative, disagreement, and not-responding.

@@

The network model architecture is shown in Figure (1).

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{architecture-cjrc.pdf}}
\end{center}
   \caption{The Machine Reading Comprehension Network Architecture for the China Judicial Reading Comprehension task.}
\label{fig:short}
\end{figure*}

@@

    There are 39333 training records, 6000 development records, and 6000 test records in the CJRC2019 dataset,
and there are 5053 training records and 1565 test records in the CJRC2020 dataset.
    The CJRC2020 followed the same format as this paper proposed, however, the annotation records has limit size, thus, I focus on the revised CJRC2019 dataset.

@@

Then from the output of the start, and the end position tensors, the maximum possible start and end position were calculated
using the positional probability addition of the all possible start-end pairs.

@@

After the encoding layers, the hidden layers of the BERT layers are kept, and the last two layers are concatenated and connected to
two Fully Connected layers for the starting index, and the ending index for the answer span indices in the context.

Recall that \citet{Sabour2017Dynamic} proposed the Capsules which are convolutions with the block non-linearity and routing, with fewer parameters than convolutional layers,
try to build better model hierarchical relationships inside of internal knowledge representation.

In general, the Capsule Net architecture in the model contains six components: three convolutional layers, the concatenating layer, the primary capsule layer, the flatten capsule layer,
the compression layer, and the fully connecting capsule layer.

@@

@@

Three losses were added with weight and then use the stochastic gradient descent to train the network parameters.
The start position loss, the end position loss, the type loss, and the supporting sentence loss were added with weighted.
The start and end loss use the Cross Entropy Loss function, the type uses binary cross entropy with logits,
and the support loss used the binary cross entropy with logits between the output and the gold value, then get the mean of each record.
The support loss has a weight of 5 for its importance in finding the destination answer span, and all other loss has the weight of 1.
And the threshold for the supporting sentence is 0.5.
The learning rate is $5e{-5}$ for the RBT3 and XLNet model, learning rate is $5e{-4}$ for the RoBERTa model, the dropout rate is 5\%, the document max sequence length for the document(the question and the context) is 512, and the max sequence length for the question is 45, the epoch size is 10.
The batch size is 16 for the RBT3, RoBERTa, XLNet model.

For the RoBERTa and XLNet model, I use the gradient accumulation steps for the training, the loss are accumulated between batches,
and every two batches, the backward result was calculated.
In this way, the large pretrained models, such as RoBERTa and XLNet, were able to be trained on the Nvidia V100 16GB of memory.

@@

 The CJRC2019 dataset proposed by \citet{duan2019cjrc} lacks the supporting sentence annotations.
For the multiple questions in one paragraph, I use the answer starting position as anchors to retrieve
the attentional subparagraph, and use the 512 characters subparagraph containing the answer as the revised context.
Also, I use the answer occurrence in the sentence as the flag to annotate the supporting sentences.

\subsection{Results}

As Table (1) shows, on the CJRC2019 development dataset, the RBT3 model achieved 39.65\% of the F1 score on the span and 36.84\% of the F1 score on the supporting sentence.
And the RoBERTa model improved performance significantly for the 12 layers of transformers, comparing to RBT3's 3 layers,
achieved 44.37\% of the F1 score on the span and 48.00\% of the F1 score on the supporting sentence.
The XLNet model achieved the best performance with 45.94\% of th F1 score on the span, and 49.35\% F1 score on the supporting sentence.

\begin{table}
\centering
\begin{tabular}{cccc}
\hline
\textbf{Model} & \textbf{Layers}& \textbf{span-F1} & \textbf{sup-F1} \\
\hline
RBT3 & 3 & 39.65\% & 36.86\% \\
RoBERTa & 12 & 44.37\% & 48.00\% \\
XLNet & 12 & 45.94\% & 49.35\% \\
\hline
\end{tabular}
\caption{Comparison of the pre-trained language models on the CJRC2019 Machine Reading Comprehension validation task.}
\end{table}

@@

In this paper, I introduced a novel Chinese Reading Comprehension model for Court Cases, which leveraging hierarchical layers of the document encoding layers.
By making use of the Capsule Net layers, the multi task model predicts the starting and ending span index, and the supporting sentence indices in the context.
Proposed model achieved 1.57\% improvement on the span F1-score and 1.35\% on the supporting sentence F1-score comparing to the BERT model in the CJRC2019 validation dataset.

\bibliographystyle{acl_natbib}
\bibliography{anthology,acl2021,acl_comprehension}
